The Shot Predictor

### 2022-10-17 Papers/PaperForReview.tex
related works for basketball postures

\author{Laith Altarabishi\\
University of Texas at Austin\\
{\tt\small laithaustin@utexas.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Sidharth Babu\\
University of Texas at Austin\\
{\tt\small sidharth.n.babu@utexas.edu}
\and
Afnan Mir \\
University of Texas at Austin\\
{\tt\small afnanmir@utexas.edu}
\and
Zayam Tariq \\
University of Texas at Austin\\
{\tt\small <insert email>}
}
\maketitle

@@

>>>>

\author{Laith Altarabishi\\
University of Texas at Austin\\
{\tt\small laithaustin@utexas.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Sidharth Babu\\
University of Texas at Austin\\
{\tt\small sidharth.n.babu@utexas.edu}
\and
Afnan Mir \\
University of Texas at Austin\\
{\tt\small afnanmir@utexas.edu}
\and
Zayam Tariq \\
University of Texas at Austin\\
{\tt\small zayamtariq@utexas.edu}
}
\maketitle

@@

Before a posture recognition algorithm can be made, though, there needs to be an understanding of what postures we are trying to recognize [1]. One example solution is shown below. 
%
\begin{quotation}
  Level 1: Divide posture into two categories based on whether or not the motion is cyclic \\
  \indent - Instantaneous Movement 
  \indent - Continuous Movement 
  \newline
  \indent Level 2: Divide posture into seven postures \\
  \indent - Walking 
  \indent - Running 
  \indent - Dribbling 
  \indent - Jumping 
  \indent - Shooting 
  \indent - Passing 
  \indent - Catching 
\end{quotation}
%

Notice how these actions are exclusive to basketball. The algorithm is only concerned with basketball, and will deem all other actions as unnecessary as such.
